---
title: "Study NBI-1070770-1747 Cohort X PK Report"
output: html_document
date: "2022-07-28"
---

Phase 1, Randomized, Placebo-Controlled, Double-Blind, Ascending Single-Dose and Multiple-Dose, and Food Effect Study to Evaluate the Safety, Tolerability, Pharmacokinetics, and Pharmacodynamics of NBI-1070770 in Healthy Subjects

This is the PK report for Study NBI-1070770-1747 Cohort X. 

Dose Level: XXX mg single dose


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

######  Set up

rm(list = ls())

# library
library(tidyverse)
library(magrittr)
library(gridExtra)
library(Hmisc)

# load data
getwd()



# final parameter file from NCA
a1 <- read.csv("Final_Parameters_Pivoted.csv",header = TRUE,stringsAsFactors = FALSE)

# concentration data
c1 <- read.csv("PKconc.csv", header = TRUE, stringsAsFactors = FALSE)

# aesthetics for plotting
size<- theme(axis.title.x=element_text(size=18), 
             axis.text.x=element_text(size=14), 
             axis.title.y=element_text(size=18),
             axis.text.y=element_text(size=14), 
             legend.text=element_text(size=14),
             legend.title=element_text(size=18),
             plot.title=element_text(size=18),
             strip.text.x=element_text(size=18),
             strip.text.y=element_text(size=18))

```


## PK Concentration

Mean concentration versus time profiles for NBI-1070770 are presented in linear scale:

```{r mean plot, echo=FALSE}
p1<-ggplot(data=c1,
           aes(x=TPTNOM,y=CONC, group=interaction(as.character(SUBJECT),as.character(DOSE)),color=as.character(DOSE)))+
  
  # individual lines, to remove comment out geom_line()+ with # in front
  geom_line()+
  
  # mean and + SD lines
  stat_summary(aes(group=as.character(DOSE), color=as.character((DOSE))),fun=mean,geom="line",size=1.2)+
  stat_summary(aes(group=as.character(DOSE), color=as.character((DOSE))),fun.min=mean,fun.max=function(x) mean(x) + sd(x),geom="errorbar",size=1)+
  
  # labeling of axes and legend
  labs(x="Nominal Time (hours)",
       y="Concentration (ng/mL)",
       color="Dose (mg)")+
  # additional aesthetics
  theme_bw()+
  size

p1

```

and log scale:

```{r mean log plot, echo=FALSE}

p1log<-p1+scale_y_continuous(trans='log10')
p1log

```

Mean (SD) are represented in thick line(s) by dose. Individual profile are represented in thin lines by dose.


Individual concentration versus time profiles for NBI-1070770 are presented in linear scale:

```{r indiv plot, echo=FALSE}
p1a<-ggplot(data=c1,
            aes(x=TPTNOM,y=CONC))+
  geom_line()+
  geom_point()+
  
  # Dose on the right banner, subject ID on the top banner
  facet_grid(as.character(DOSE)~as.character(SUBJECT))+
  labs(x="Nominal Time (hours)",
       y="Concentration (ng/mL)")+
  theme_bw()
p1a

```

and log scale:

```{r indiv plot log, echo=FALSE}
p1alog<-p1a+scale_y_continuous(trans='log10')
p1alog

```


## PK Parameter


Summary of PK parameters by dose is presented as follows:

```{r parm summary, echo=FALSE}
library(tidyr)
library(knitr)

# Functions
# n count
n3 = function(x){
  (length(x)) - (sum(is.na(x)))
}

# Geometric mean
gm_mean<-function(x,na.rm=T){
  a <- mean(log(x[x>0]),na.rm=T)
  exp(a)
}

# Geometric CV%
geocv<-function(x, na.rm = TRUE){
  sdlog <- sd(log(x[x > 0]), na.rm = na.rm)
  geosd <- exp(sdlog)
  100*(sqrt(exp(log(geosd)^2)-1))
}

# Rename and select PK parameters to report
# Currently does not include dose normalized Cmax of AUC, to add in subsequent cohorts.
pk1<-a1 %>% mutate("Cmax (ng/mL)" = Cmax,
                   "tmax (h)" = tmax,
                   "tlag (h)" = Tlag,
                   "AUCtlast (ng*h/mL)" = AUC0_tlast,
                   "AUCinf (ng*h/mL)" = AUC0_inf,
                   "AUC%extrap (%)"=AUC_.Extrap_obs,
                   "t1/2 (h)" = t1_2,
                   "lambda_z (1/h)" = Lambda_z,
                   "CL/F (L/h)" = CL_F,
                   "Vz/F (L)" = Vz_F) %>% 
  select(DOSE, SUBJECT,"Cmax (ng/mL)", "tmax (h)", "tlag (h)",
         "AUCtlast (ng*h/mL)", "AUCinf (ng*h/mL)", "AUC%extrap (%)", 
         "t1/2 (h)", "lambda_z (1/h)", "CL/F (L/h)", "Vz/F (L)")


# make the table longer by placing parameters on one column and values on another
pksum<-pivot_longer(data=pk1,
                    cols= "Cmax (ng/mL)":"Vz/F (L)",
                    names_to="Parameter",
                    values_to="Value",
                    values_drop_na=TRUE)


# summarize by parameter and dose
pksum1<-pksum %>% 
  group_by(DOSE, Parameter)%>% 
  #group_by(Parameter) %>% 
  summarise_at(vars( Value), #"Cmax (ng/mL)":"Vz/F (L)"),
            list(Mean = mean,
                 Stdev = sd,
                 Min = min,
                 Median = median,
                 Max = max,
                 Gmean = gm_mean,
                 "Gcv%" = geocv)) %>% 
  rename("Dose (mg)" = DOSE) %>% 
  arrange(Parameter)

# ensures no conversion to scientific notation and 3 digits after decimal
options(scipen = 999, digits=3)

# output as a table in the report
kable(pksum1)


```




## Exposures and NOAEL

For all cohorts, dose increases will not exceed a 3.34-fold increase from the highest previously administered single dose and will not exceed the dose projected to achieve the mean steady-state maximum plasma concentration (Cmax) and area under the plasma concentration versus time curve (AUC) values associated with NOAEL in the male rats (most sensitive species) 28-day Good Laboratory Practices (GLP) toxicity studies (Cmax: 27,300 ng/mL; AUC: 121,000 ng×h/mL).


The fold-change against the NOAEL based on the mean Cmax for the current dose level is:

```{r noael cmax, echo=TRUE}

  (27300-350.500)/350.500

```


The fold-change against the NOAEL based on the mean AUCinf for the current dose level is:

```{r noael auc, echo=TRUE}

  (121000-12981.297)/12981.297

```


